### 2018-09-25 Sections/essay_NISQ_QC.tex
minor changes

\section{Noise-Intermediate-Scale Quantum technology (NISQ)}

@@

\subsection{Quantum simulation}
As it has been stressed previously, quantum computers are very well suited for studying highly entangled systems of many particles. It is the natural platform to simulate highly entangled states, which is where quantum computers appear to have a clear advantage over classical ones.

@@

We may be able to study quantum dynamics using NISQ: one example is quantum chaos, systems in which entanglement spreads very rapidly. Classical computers are particularly inefficient at simulating quantum dynamics, and here quantum computers have an especially obvious advantage. Insights can be gained using noisy devices with orders of 100's of qubits.

>>>>

\section{Noisy-Intermediate-Scale Quantum technology (NISQ)}

@@

\subsection{Quantum dynamics}
As it has been stressed previously, quantum computers are very well suited for studying highly entangled systems of many particles. It is the natural platform to simulate highly entangled states, which is where quantum computers appear to have a clear advantage over classical ones.

@@

Classical computers are particularly inefficient at simulating quantum dynamics, i.e how highly entangled quantum states will evolve time. Here quantum computers have an especially obvious advantage. One example we may be able to study using NISQ is quantum chaos. In these systems entanglement spreads very rapidly. Insights can be gained using noisy devices with orders of 100's of qubits.
